Supporting Information

### 2018-03-20 SupportingInformation.Rmd
cannot remember what I changed

    shold<-tl_stats(ss[,,sc])
    spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
    rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
    spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
  }
}
names(kend.stats.res)<-names(kend.surrog)
names(kend.points.res)<-names(kend.surrog)
names(spea.stats.res)<-names(spea.surrog)
names(spea.points.res)<-names(spea.surrog)

#DAN: now you want to compare whether tl held, and the slope (statistically and visually)
#across the different elements of kend.XX.res and spea.XX.res. See drawing of a figure layout on desk.

>>>>

    shold<-tl_stats(ss[,,sc])
    spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
    rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
    spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
  }
}
names(kend.stats.res)<-names(kend.surrog)
names(kend.points.res)<-names(kend.surrog)
names(spea.stats.res)<-names(spea.surrog)
names(spea.points.res)<-names(spea.surrog)
```

<!--Now make some plots-->
```{r taylor_plots, echo=T}
#plot TL for clayton
xlimits<-range(kend.points.res[[1]][,1,],kend.points.res[[2]][,1,],kend.points.res[[3]][,1,],kend.points.res[[4]][,1,])
ylimits<-range(kend.points.res[[1]][,2,],kend.points.res[[2]][,2,],kend.points.res[[3]][,2,],kend.points.res[[4]][,2,])
par(mfrow=c(1,1))
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for normal copula
plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for frank
plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```

```{r, echo=T}
#plot TL for survival clayton
plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits)  
```
